More than one Author with different Affiliations

### 2012-06-04 paper/ms.tex
Bullet points
Show test cases
Green ref

\section{Probabilistic Catalogs}

@@

@@

\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Brewer, P{\'a}rtay, 
\& Cs{\'a}nyi}{2011b}]{dnest} Brewer B.~J., P{\'a}rtay L.~B.,
Cs{\'a}nyi G., 2011, Statistics and Computing, 21, 4, 649-656. arXiv:0912.2380

>>>>

\section{Probabilistic Catalogs}
\begin{itemize}
\item Catalogs as models for what's out there \\
\item Standard techniques for constructing catalogs, and under what
cicrumstances they stop working \\
\item 
\end{itemize}

@@

\begin{figure}
\hspace{-1cm}
\includegraphics{Figures/test_cases.eps}
\end{figure}

@@

\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Brewer, P{\'a}rtay, 
\& Cs{\'a}nyi}{2011}]{dnest} Brewer B.~J., P{\'a}rtay L.~B.,
Cs{\'a}nyi G., 2011, Statistics and Computing, 21, 4, 649-656. arXiv:0912.2380

\bibitem[\protect\citeauthoryear{Green}{1995}]{rjmcmc}
Green, P.~J., 1995, Reversible Jump Markov Chain Monte Carlo Computation and Bayesian Model Determination, Biometrika 82 (4): 711–732.
